Appendix

### 2020-03-04 manuscript/appendix.Rmd
resize scatter plot

```{r ag-scatter, fig.cap="Lake nutrient concentrations plotted against percent watershed agriculture.", fig.width = 5, fig.height = 3.2, warning=FALSE, message=FALSE}
dt <- readRDS("../data/dt.rds")

>>>>

```{r ag-scatter, fig.cap="Lake nutrient concentrations plotted against percent watershed agriculture.", fig.width = 5.5, fig.height = 3, warning=FALSE, message=FALSE}
dt <- readRDS("../data/dt.rds")
